On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 tt_theorem.tex
12/3 d=3 cont.

\begin{lemma}
\label{TTT_a4_2b_lemma}
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
When a bead is stabilized by bond, it forms at least two bonds.
\end{lemma}

\begin{proof}%[proof of lemma]
Suppose $w[i]$ were stabilized by only one bond. See Fig.~\ref{TTT_a4_lemma_fig}. If $n_3$ is free, $w[i-2]$ still has some bonds because of arity $\alpha = 4$. Thus, $n_4$ must be occupied; otherwise, $w[i]$ would be stabilized nondeterministically at $n_3$ and $n_4$. Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$. $n_1$ has some hands because $n_3$ is free. Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands. It contradict assumption.
\end{proof}

@@

\begin{proof}
According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds. Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized. See Fig.\ref{TTT_a4_first}. any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$. At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind. In this case, a point which is able to put a bead is only $n_2$. Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$. Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
\end{proof}

@@

@@

\begin{lemma}
\label{TTT_a3_2b_lemma}
 Let $p$ be a point whose neighbors is occupied at least two point. If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
\end{lemma}

\begin{proof}[proof of lemma]
Assume the transcript is stabilized until $w[i-1]$. One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$. If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond. Then, any neighbors do not have bond without $w[i-1]$. Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$. In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$. one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$. Then, any neighbors of $p$ are occupied. That is, if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
\end{proof}

>>>>

%\begin{lemma}
%\label{TTT_a4_2b_lemma}
%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
%When a bead is stabilized by bond, it forms at least two bonds.
%\end{lemma}
%
%\begin{proof}%[proof of lemma]
%Suppose $w[i]$ were stabilized by only one bond. See Fig.~\ref{TTT_a4_lemma_fig}. If $n_3$ is free, $w[i-2]$ still has some bonds because of arity $\alpha = 4$. Thus, $n_4$ must be occupied; otherwise, $w[i]$ would be stabilized nondeterministically at $n_3$ and $n_4$. Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$. $n_1$ has some hands because $n_3$ is free. Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands. It contradict assumption.
%\end{proof}

@@

\begin{proof}
%According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds. Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized. See Fig.\ref{TTT_a4_first}. any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$. At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind. In this case, a point which is able to put a bead is only $n_2$. Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$. Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
%%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
seki sensei.
\end{proof}

@@

\begin{lemma}
\label{TTT_a3_2b_lemma}
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. 
If $S[i] = t$ or $t^\times$ and $S[i+1] \neq \blacksquare$, then the bead $w[i]$ consumes also at least one bond. 
% Let $p$ be a point whose neighbors is occupied at least two point. If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
\end{lemma}

\begin{proof}%[proof of lemma]
Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
Suppose $w[i]$ were stabilized without any bond.
Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
That is, $n_1$ is occupied.
We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed

%One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$. If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond. Then, any neighbors do not have bond without $w[i-1]$. Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$. In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$. one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$. Then, any neighbors of $p$ are occupied. That is, if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
\end{proof}

@@
